Dashboards for stock assessments: Getting started

### 2019-10-17 analysis/dashboards/getting_started.Rmd
Draft an rmarkdown basics page in the getting_started dashboard

@@

- A graphing package that works like other R plots expect it produces interactive visualizations
- The package allows the user to create interactive web graphics from [**ggplot2**](https://ggplot2.tidyverse.org/) graphs
- Also provides a more 'direct' link to the core [plotly.js](https://plot.ly/javascript/) JavaScript library using syntax inspired by the grammar of graphics

@@

1. A YAML header surrounded by `----`
2. R code chunks surrounded by `` ``` ``
3. Text following `markdown` formatting

@@

>>>>

<style>
h5 {display: inline;}
</style>

@@

- A graphing package that works like other R plots except it produces interactive visualizations
- The package allows the user to create interactive web graphics from [**ggplot2**](https://ggplot2.tidyverse.org/) graphs
- Also provides a more 'direct' link to the core [plotly.js](https://plot.ly/javascript/) JavaScript library using syntax inspired by the grammar of graphics

@@

1. A YAML header surrounded by `----`
2. Text following `markdown` formatting
3. R code chunks surrounded by `` ``` ``

@@

rmarkdown {data-navmenu="Basics"}
=======================================================================

Row {data-height=250}
-------------------------------------

### R markdown

The package `rmarkdown` enables the writing of `markdown` text and `R` code in the same document (extension `.Rmd`). Most R markdown files includes three types of content:

1. A YAML header surrounded by `----`
2. Text following `markdown` formatting
3. R code chunks surrounded by `` ``` ``

Row {data-height=600}
-------------------------------------

### YAML

The first step in setting up an R markdown file is to define a YAML header. In the [skeleton](#skeleton), it looks like this:

This is where the output type is defined along with other items such as title, author, date, etc. A `flex_dashboard` is requested here. There are are growing number of output types supported by R markdown (e.g. html_document, pdf_document, word_document).

### Markdown

Next, write plain text using markdown syntax to describe how to format the text in the final document.

- `Plain text` simply translates to Plain text in the default font of the output document.
- Italics and bold are specified using asterisk and/or underscores:
    - `*italic*` or `_italic_` $\rightarrow$ *italic*
    - `**bold**` or `__bold__` $\rightarrow$ **bold**
    - `**_bold-italic_** ` $\rightarrow$ **_bold-italic_** 
- Equations can be specified using LaTeX syntax:
    - `$W = \alpha L ^{\beta}$` $\rightarrow$ $W = \alpha L ^{\beta}$
- Ordered and unordered lists are generated using numbers and dashes or asterisk, respectively:
    - `1. ordered item 1` $\rightarrow$ 1. &nbsp; ordered item 1
    - `- unordered item` $\rightarrow$ • &nbsp; unordered item
- Headers are define using hashtags:
   - `##### Header 5` $\rightarrow$ <h5> Header 5 </h5>
   - Note that markdown headers with three hashtags or less have specific formatting functions in `flexdashboard`

### R

Finally, mix in `R` code by surrounding chunks of code using one backtick for inline code (e.g.`` `r knitr::inline_expr("1+1")` `` will print 2 in the output) or three backticks to run several lines of code and/or display a table or plot. The below chunk will print the top three rows of the `cars` data-set:

````
```{r} `r ''`
head_cars <- head(cars, 3)
head_cars
```
````
Resulting in the following output:

```{r}
head_cars <- head(cars, 3)
head_cars
```
